---
title: "rrBLUP Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
  word_document: default
---

```{r}
library(rrBLUP)
Markers <- as.matrix(read.table(file="SNPp.txt"), header=F)
head(Markers)
Pheno <-as.matrix(read.table(file ="Trait.txt", header=TRUE))
head(Pheno)
head (Markers)

```



Check the dimensions of the matrix
```{r}
dim(Markers)
dim(Pheno)
```


#####
#what if lots of markers are NA?
#impute with A.mat
impute=A.mat(Markers,max.missing=0.5,impute.method="mean",return.imputed=T)
Markers_impute=impute$imputed
head(Markers_impute)
dim(Markers_impute)

#remove markers with more than 50% missing data
Markers_impute2=Markers_impute[,-c(169,562)]
dim(Markers_impute)
dim(Markers_impute2)




#different number of SNP markers
Marker50 <- Markers[,sample (1:5403,400)]

train= as.matrix(sample(1:478,100))
test<- sample (setdiff(1:478,train),100)
Pheno_train=Pheno[train,]
m_train=Marker50[train,]
Pheno_valid=Pheno[test,]
m_valid=Marker50[test,]

#50
protein=(Pheno_train[,1])
Protein_answer<-mixed.solve(protein, Z=m_train, K=NULL, SE = FALSE, return.Hinv=FALSE)
YLD = Protein_answer$u
e = as.matrix(YLD)
pred_yield_valid =  m_valid %*% e
pred_yield=(pred_yield_valid[,1])+Protein_answer$beta
pred_yield
yield_valid = Pheno_valid[,1]
YLD_accuracy <-cor(pred_yield_valid, yield_valid, use="complete" )
YLD_accuracy 

#end of test of SNP marker







#####
#######
#define the training and test populations
#training-60% validation-40%
train= as.matrix(sample(1:478,100))
test<- sample (setdiff(1:478,train),100)
Pheno_train=Pheno[train,]
m_train=Markers_impute[train,]
Pheno_valid=Pheno[test,]
m_valid=Markers_impute[test,]

########
protein=(Pheno_train[,1])
Protein_answer<-mixed.solve(protein, Z=m_train, K=NULL, SE = FALSE, return.Hinv=FALSE)
YLD = Protein_answer$u
e = as.matrix(YLD)
pred_yield_valid =  m_valid %*% e
pred_yield=(pred_yield_valid[,1])+yield_answer$beta
pred_yield
yield_valid = Pheno_valid[,1]
YLD_accuracy <-cor(pred_yield_valid, yield_valid, use="complete" )
YLD_accuracy 

PHT_HT=(Pheno_train[,2])
PHT_HT_answer<-mixed.solve(PHT_HT, Z=m_train, K=NULL, SE = FALSE, return.Hinv=FALSE)
PHT_HT = PHT_HT_answer$u
e = as.matrix(PHT_HT)
pred_PHT_HT_valid =  m_valid %*% e
PHT_HT_valid = Pheno_valid[,2]
PHT_HT_accuracy <-cor(pred_PHT_HT_valid, PHT_HT_valid, use="complete" )
PHT_HT_accuracy 

HD_DATE=(Pheno_train[,3])
HD_DATE_answer<-mixed.solve(HD_DATE, Z=m_train, SE = FALSE, return.Hinv=FALSE)
HD_DATE = HD_DATE_answer$u
e = as.matrix(HD_DATE)
pred_HD_DATE_valid =  m_valid %*% e
HD_DATE_valid = Pheno_valid[,3]
HD_DATE_accuracy <-cor(pred_HD_DATE_valid, HD_DATE_valid, use="complete" )
HD_DATE_accuracy 


#### cross validation for many cycles for yield only
traits=1
cycles=100
accuracy = matrix(nrow=cycles, ncol=traits)
for(r in 1:cycles)
{
train= as.matrix(sample(1:478,350))
test<- sample (setdiff(1:478,train),100)
Pheno_train=Pheno[train,]
m_train=Markers_impute[train,]
Pheno_valid=Pheno[test,]
m_valid=Markers_impute[test,]

yield=(Pheno_train[,1])
yield_answer<-mixed.solve(yield, Z=m_train, K=NULL, SE = FALSE, return.Hinv=FALSE)
YLD = yield_answer$u
e = as.matrix(YLD)
pred_yield_valid =  m_valid %*% e
pred_yield=(pred_yield_valid[,1])+yield_answer$beta
pred_yield
yield_valid = Pheno_valid[,1]
accuracy[r,1] <-cor(pred_yield_valid, yield_valid, use="complete" )
}
mean(accuracy)

write.csv (accuracy, file= "validation350.csv")


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
